	\begin{thebibliography}{9}

	\bibitem{tf}
		Martín Abadi, Ashish Agarwal, Paul Barham, Eugene Brevdo,
Zhifeng Chen, Craig Citro, Greg S. Corrado, Andy Davis,
Jeffrey Dean, Matthieu Devin, Sanjay Ghemawat, Ian Goodfellow,
Andrew Harp, Geoffrey Irving, Michael Isard, Rafal Jozefowicz, Yangqing Jia,
Lukasz Kaiser, Manjunath Kudlur, Josh Levenberg, Dan Mané, Mike Schuster,
Rajat Monga, Sherry Moore, Derek Murray, Chris Olah, Jonathon Shlens,
Benoit Steiner, Ilya Sutskever, Kunal Talwar, Paul Tucker,
Vincent Vanhoucke, Vijay Vasudevan, Fernanda Viégas,
Oriol Vinyals, Pete Warden, Martin Wattenberg, Martin Wicke,
Yuan Yu, and Xiaoqiang Zheng.
TensorFlow: Large-scale machine learning on heterogeneous systems,
2015. Software available from tensorflow.org.

	\bibitem{jupyter}
		Kluyver, Thomas, Ragan-Kelley, Benjamin, Pérez, Fernando, Granger, Brian, Bussonnier, Matthias, Frederic, Jonathan, Kelley, Kyle, Hamrick, Jessica, Grout, Jason, Corlay, Sylvain, Ivanov, Paul, Avila, Damián, Abdalla, Safia, Willing, Carol and [Unknown], Jupyter development team (2016) Jupyter Notebooks – a publishing format for reproducible computational workflows. Loizides, Fernando and Scmidt, Birgit (eds.) In Positioning and Power in Academic Publishing: Players, Agents and Agendas. IOS Press. pp. 87-90. (doi:10.3233/978-1-61499-649-1-87).
		
	\bibitem{adam}
		arXiv:1412.6980 


	\bibitem{weight_decay}
	Krogh, Anders \& Hertz, J. (1992). A Simple Weight Decay Can Improve Generalization. Adv. Neural Inform. Process Systems. 4. 

	\bibitem{pubchem}
		Kim S, Thiessen PA, Bolton EE, Chen J, Fu G, Gindulyte A, Han L, He J, He S, Shoemaker BA, Wang J, Yu B, Zhang J, Bryant SH. PubChem Substance and Compound databases. Nucleic Acids Res. 2016 Jan 4; 44(D1):D1202-13. Epub 2015 Sep 22 [PubMed PMID: 26400175] doi: 10.1093/nar/gkv951
		
	\bibitem{gdb}
		J. Chem. Inf. Model.  52, 11, 2864-2875		

	\bibitem{pubchemqc}
		J. Chem. Inf. Model.  57, 6, 1300-1308

	\bibitem{sklearn}
		Scikit-learn: Machine Learning in Python, Pedregosa et al., JMLR 12, pp. 2825-2830, 2011

	\bibitem{universal_approx}
		K. Hornik, M. Stinchcombe, and H. White, Multi-layer feedforward networks are universal 	approximators, preprint, 1988. 
		
	\bibitem{mg} Kearnes, S., McCloskey, K., Berndl, M., Pande, V., \& Riley, P.\ 2016, Journal of Computer-Aided Molecular Design, 30, 595 
	
	\bibitem{jctc_prediction}
		J. Chem. Theory Comput.  13, 11, 5255-5264
	
	\bibitem{rdkit} RDKit : Open-source cheminformatics. www.rkdit.org. [accessed 11-April-2013]
	
	\bibitem{graph_fingerprint}
		arXiv:1509.09292 [cs.LG]
	
	

	
          
\end{thebibliography}